COSC-373 Final Report: Bitcoin

### 2022-05-11 paper/paper.tex
Add overview of Bitcoin.

\title{COSC-373: Bitcoin}
\author{Lee Jiaen, Hyery Yoo, and Alexander Lee}

@@

>>>>

\title{COSC-373 Final Report: Bitcoin}
\author{Lee Jiaen, Hyery Yoo, and Alexander Lee}

@@

The \emph{Bitcoin network} is a randomly connected overlay network of a few
thousand nodes, where nodes are controlled by various owners and perform the
same operation. In other words, the network is a homogeneous network without
central control. Each user of Bitcoin generates a private/public key pair. A
user is identified by their \emph{address}, which is derived from their public
key and used to receive funds in Bitcoin. All nodes in the Bitcoin network work
together to track each address' balance in bitcoins.
